Accounting for sampling error in when applying matrix factorization to gene expression data

### 2021-01-24 Methods_Paper.tex
Copied images, inputs and .bib to directory so self-contained * All required images copied from HgsocTromics/Plots/... to ./images * All required .tex inputs copied to ./inputs * Methods_Paper.tex edited to use local copies above * OvarianCancer.bib copied directly (was a symbolic link)

\documentclass[tikz, 11pt,a4paper,oneside,fleqn, draft]{article}

@@

\graphicspath{{/home/ipoole/Documents/gitrepos/MScDissertation/images/}}  % trailin '/' is required!
\newcommand{\plotspath}[1]{{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/#1}}

@@

\def\S{0.4}
\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_fixed.pdf}} \\
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_bootstrap.pdf}}\\
\caption{Clustering of metagenes from ICA facorizations on the N=80 AOCS dataset, comparing \emph{fixed} sampling (top row) with \emph{bootstrap} sampling (bottom row) for a selection of factorization ranks.  }
\label{fig-AOCS-ica-fixed-vs-bootstrap}
\label{fig-first-cluster-result}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_fixed.pdf}} 
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}}
\caption{Clustering of metagenes from ICA facorizations on the N=374 TCGA dataset, again comparing fixed and bootstrap sampling.}
\label{fig-TCGA-ica-fixed-vs-bootstrap}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_NMF_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_PCA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=0.55]{\plotspath{/TCGA_OV_VST/FactorClustering/silhouette_plots_TCGA_2_3_4_5_6_7_8_9_10_bootstrap.pdf}} 
\caption{Metagene clustering for all three methods applied to the N=374 TCGA dataset with bootstrap sampling, over a range of factorization ranks.  The silhouette scores are also plotted (bottom).  It is on the basis of this figure that the factorization ranks for each method were selected.}
\label{fig-TCGA-all-bootstrap}
\label{fig-last-cluster-result}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.08]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF-1} \\
\end{center}
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components NMF-1  In these diagrams, enriched terms are coloured purple, while there ancestors in the ontology are yellow.  }
\label{fig-NMF_1-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.1]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_2_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_2_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF 2} \\
\caption{Lineage maps of enriched GO terms for components NMF-2.   (NMF-3 produced no significant enrichment results)}
\label{fig-NMF_2-go-lineage}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.09]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-3} \\
\end{center}
\caption{Lineage maps of enriched GO terms for components ICA-3}
\label{fig-ICA-3-5-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.06]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_5_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_5_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-5} \\
\caption{Lineage maps of enriched GO terms for components ICA-5}
\label{fig-ICA-5-5-go-lineage}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.4 \textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-1} \\
\end{center}
\caption{Lineage maps of enriched GO terms for component PCA-1  }
\label{fig-PCA-1-3-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width= 0.7\textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-3} \\
\end{center}
\caption{Lineage maps of enriched GO terms for component PCA-3. (Component PCA-2 produced no significant enrichment results)  }
\label{fig-PCA-3-3-go-lineage}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.45]{\plotspath{BoxAndScatters/genomic_feature_scatters_TCGA_AOCS.pdf}} 
\caption{Grid of scatter plots to visualise the correlation between metasamples and genomic features.  In the case of WGD which has binary values (0, 1), jitter is applied for visual effect only.   Above each plot is shown a correlation coefficient $r$ and associated p-value, highlighted with '***' where $p < 0.01$.  In the case of WGD , the Point-Biserial correlation is used; for all others Pearson's $r$ is used.}
\label{fig-genomic-scatters}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.4,draft=false]{\plotspath{HeatMaps/clustered_heatmap_BOTH_BOTH.pdf}} 
\end{center}
\caption{Heatmap of the metasamples matrix for the combined AOCS + TCGA dataset.  The 'Which' field indicates the source dataset; purple: AOCS, yellow:TCGA.}
\label{fig-heatmap-BOTH}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.36]{\plotspath{BoxAndScatters/wgd_boxplot_NMF_BOTH_BOTH.pdf}}
\includegraphics[scale=0.36]{\plotspath{BoxAndScatters/wgd_boxplot_ICA_BOTH_BOTH.pdf}}
\includegraphics[scale=0.36]{\plotspath{BoxAndScatters/wgd_boxplot_PCA_BOTH_BOTH.pdf}}

\end{center}
\caption{Boxplots of metasamples from the combined AOCS + TCGA datasets, showing relationship between metasamples dataset origin; Which=0 or 1 for AOCS or TCGA respectively.}
\label{fig-boxplots-BOTH}
\end{figure}

>>>>

\documentclass[tikz, 11pt,a4paper,oneside,fleqn]{article}

@@

\graphicspath{{/home/ipoole/Documents/gitrepos/MScDissertation/images/}}  % trailing '/' is required!

@@

\def\S{0.4}
\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_fixed.pdf} \\
\includegraphics[scale=\S]{multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_bootstrap.pdf}\\
\caption{Clustering of metagenes from ICA facorizations on the N=80 AOCS dataset, comparing \emph{fixed} sampling (top row) with \emph{bootstrap} sampling (bottom row) for a selection of factorization ranks.  }
\label{fig-AOCS-ica-fixed-vs-bootstrap}
\label{fig-first-cluster-result}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_fixed.pdf} 
\includegraphics[scale=\S]{multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}
\caption{Clustering of metagenes from ICA facorizations on the N=374 TCGA dataset, again comparing fixed and bootstrap sampling.}
\label{fig-TCGA-ica-fixed-vs-bootstrap}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=\S]{multiple_single_factors_scatter_TCGA_NMF_2_3_5_10_bootstrap.pdf} \\
\includegraphics[scale=\S]{multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf} \\
\includegraphics[scale=\S]{multiple_single_factors_scatter_TCGA_PCA_2_3_5_10_bootstrap.pdf} \\
\includegraphics[scale=0.55]{silhouette_plots_TCGA_2_3_4_5_6_7_8_9_10_bootstrap.pdf} 
\caption{Metagene clustering for all three methods applied to the N=374 TCGA dataset with bootstrap sampling, over a range of factorization ranks.  The silhouette scores are also plotted (bottom).  It is on the basis of this figure that the factorization ranks for each method were selected.}
\label{fig-TCGA-all-bootstrap}
\label{fig-last-cluster-result}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.08]{go_lineage_1_of_NMF_3.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_1_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF-1} \\
\end{center}
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components NMF-1  In these diagrams, enriched terms are coloured purple, while there ancestors in the ontology are yellow.  }
\label{fig-NMF_1-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.1]{go_lineage_2_of_NMF_3.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_2_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF 2} \\
\caption{Lineage maps of enriched GO terms for components NMF-2.   (NMF-3 produced no significant enrichment results)}
\label{fig-NMF_2-go-lineage}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.09]{go_lineage_3_of_ICA_5.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_3_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-3} \\
\end{center}
\caption{Lineage maps of enriched GO terms for components ICA-3}
\label{fig-ICA-3-5-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.06]{go_lineage_5_of_ICA_5.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_5_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-5} \\
\caption{Lineage maps of enriched GO terms for components ICA-5}
\label{fig-ICA-5-5-go-lineage}
\end{center}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.4 \textwidth]{go_lineage_1_of_PCA_3.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_1_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-1} \\
\end{center}
\caption{Lineage maps of enriched GO terms for component PCA-1  }
\label{fig-PCA-1-3-go-lineage}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width= 0.7\textwidth]{go_lineage_3_of_PCA_3.png} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{inputs/TCGA_go_gene_set_3_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-3} \\
\end{center}
\caption{Lineage maps of enriched GO terms for component PCA-3. (Component PCA-2 produced no significant enrichment results)  }
\label{fig-PCA-3-3-go-lineage}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.45]{genomic_feature_scatters_TCGA_AOCS.pdf}
\caption{Grid of scatter plots to visualise the correlation between metasamples and genomic features.  In the case of WGD which has binary values (0, 1), jitter is applied for visual effect only.   Above each plot is shown a correlation coefficient $r$ and associated p-value, highlighted with '***' where $p < 0.01$.  In the case of WGD , the Point-Biserial correlation is used; for all others Pearson's $r$ is used.}
\label{fig-genomic-scatters}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.4,draft=false]{clustered_heatmap_BOTH_BOTH.pdf}
\end{center}
\caption{Heatmap of the metasamples matrix for the combined AOCS + TCGA dataset.  The 'Which' field indicates the source dataset; purple: AOCS, yellow:TCGA.}
\label{fig-heatmap-BOTH}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[scale=0.36]{wgd_boxplot_NMF_BOTH_BOTH.pdf}
\includegraphics[scale=0.36]{wgd_boxplot_ICA_BOTH_BOTH.pdf}
\includegraphics[scale=0.36]{wgd_boxplot_PCA_BOTH_BOTH.pdf}
\end{center}
\caption{Boxplots of metasamples from the combined AOCS + TCGA datasets, showing relationship between metasamples dataset origin; Which=0 or 1 for AOCS or TCGA respectively.}
\label{fig-boxplots-BOTH}
\end{figure}
